Multi-Agent Pathfinding with Matching using Increasing Cost Tree Search

### 2021-06-26 docs/paper.tex
Extended future work section

	\begin{property}[Monotonicity]
		\label{monotonicity}
		In bounded exhaustive search using ICTS, solving the matchings in increasing order of root SIC makes the effort $\Delta_{m,\text{bounded}}$ monotonically non-increasing as a function of $m$.
	\end{property}
	\begin{proof}
		Due to the order of matchings for successive matchings $m,m+t$ for some $t\geq 1$, $C^*_{m} \leq C^*_{m+t}$. By definition, $B_{m+2} = \min(B_{m+1},C_{m+1})$ meaning that $B_{m+2} \leq B_{m + 1}$ so transitively $B_{m+t+1} \leq B_{m+1}$. Therefore
		\[B_{m+t+1} - C^*_{m+t}\leq B_{m+1} - C^*_m\implies \Delta_{m+t,\text{bounded}} \leq \Delta_{m,\text{bounded}}\]
	\end{proof}
	\begin{property}[Conditional optimality]
		\label{cond-monoton-optim}
		Assuming that $\Delta_m$, the unbounded effort, is monotonically non-decreasing as a function of $m$ (with $m$ in increasing order of $C^*_m$), ordered enumeration minimizes the total number of nodes searched across matchings.
	\end{property}
	\subsubsection{Approximate ordered enumeration}
	In practice, it is difficult to enumerate all matchings in increasing order of root SIC. Finding a lowest SIC $m$ reduces to the assignment problem that can be solved using the Hungarian algorithm \cite{kuhn55} in polynomial time; however, to the knowledge of the author, no algorithm exists to more generally compute the $i$'th matching in increasing order of $C^*_m$ (assuming some fixed tie-breaking). This means that matchings have to be exhaustively enumerated and stored in memory to sort them, but this requires $\mathcal{O}(M)$ memory which was found to be more problematic in practice than the time complexity of the sorting, $\mathcal{O}(M\log(M))$.

@@

	Future research could also look into improving the ICTS-m method described using for instance more extensive pruning or properties of the problem such as lower-bounds on per-team solution SIC that can be computed using the Hungarian Algorithm. Another approach to explore would be hybridized approaches that enumerate partially constrained MAPFM instances which can be solved using any MAPFM solver. In this way, the benefit of the successive bounding of the search could be exploited and by carefully selecting agents to constrain, these constrained MAPFM instances could potentially be made relatively easy.

>>>>

	\begin{property}[Monotonicity]
		\label{monotonicity}
		In bounded exhaustive search using ICTS, solving the matchings in increasing order of root SIC makes the effort $\Delta_{m,\text{bounded}}$ monotonically non-increasing as a function of $m$.
	\end{property}
	\begin{proof}
		Due to the order of matchings for successive matchings $m,m+t$ for some $t\geq 1$, $C^*_{m} \leq C^*_{m+t}$. By definition, $B_{m+2} = \min(B_{m+1},C_{m+1})$ meaning that $B_{m+2} \leq B_{m + 1}$ so transitively $B_{m+t+1} \leq B_{m+1}$. Therefore
		\[B_{m+t+1} - C^*_{m+t}\leq B_{m+1} - C^*_m\implies \Delta_{m+t,\text{bounded}} \leq \Delta_{m,\text{bounded}}\]
	\end{proof}
	\begin{property}[Conditional optimality]
		\label{cond-monoton-optim}
		Assuming that $\Delta_m$, the unbounded effort, is monotonically non-decreasing as a function of $m$ (with $m$ in increasing order of $C^*_m$), ordered enumeration minimizes the total number of nodes searched across matchings.
	\end{property}
	\subsubsection{Approximate ordered enumeration}
	In practice, it is difficult to enumerate all matchings in increasing order of root SIC.

	Finding a lowest SIC $m$ reduces to the assignment problem that can be solved using the Hungarian algorithm \cite{kuhn55} in polynomial time;

	however, to the knowledge of the author, no algorithm exists to more generally compute the $i$'th matching in increasing order of $C^*_m$ (assuming some fixed tie-breaking). This means that matchings have to be exhaustively enumerated and stored in memory to sort them, but this requires $\mathcal{O}(M)$ memory which was found to be more problematic in practice than the time complexity of the sorting, $\mathcal{O}(M\log(M))$.

@@

	%\section{Future work}
	A key idea for future research to look into is how to exploit the lower-bound on solution SIC that can be found using the Hungarian Algorithm \cite{kuhn55}. This lower-bound could be used in a branch-and-bound \cite{land1960} search of matchings. The most straightforward way would be to use an algorithm for MAPF at leaf nodes but algorithms for MAPFM could be used to solve (small) branches. Another possibility would be to use this bound to improve ICTS-m by only executing the $k$-agent low-level search for nodes that satisfy this bound. Lower-bounding in ICTS-m could be further improved by finding the optimal SIC for the anonymous MAPF instance corresponding to each team using a similar approach as \cite{baauw2021}. As long as there is a team that does not meet its bound, branching only on agents within this team is possible without losing optimality.

	A related observation is that the algorithms introduced in this work do not rely on the property of agents and goals having one color. Both exhaustive ICTS and ICTS-m could easily be adapted to support one or more colors (teams) for each agent and goal while still guaranteeing optimality, in contrast to CBM \cite{ma2016} and its SIC adaptation \cite{baauw2021} which specifically use this property to plan single teams in polynomial time. Future research could study the multi-color MAPFM variant and the application of methods described in this work to this problem.
